---
title: "Record(Chapter-2 =>Question 8)"
author: "santhosh s"
date: "2023-09-26"
output: html_document
---

8. This exercise relates to the College data set, which can be found in
the file College.csv. It contains a number of variables for 777 different
universities and colleges in the US. The variables are


(a) Use the read.csv() function to read the data into R. Call the
loaded data college. Make sure that you have the directory set
to the correct location for the data.
```{r}
library(ISLR)
attach(College)
college<-College

View(college)

# instead of loading external csv file we have a file called College in our ISLR package 

```

(b) Look at the data using the fix() function. You should notice
that the first column is just the name of each university. We don’t
really want R to treat this as data. However, it may be handy to
have these names for later. Try the following commands:
```{r}
college<-college[,-1]
View(college)

```

(c) i. Use the summary() function to produce a numerical summary
of the variables in the data set.
```{r}
summary(college)
```

ii. Use the pairs() function to produce a scatterplot matrix of
the first ten columns or variables of the data. Recall that
you can reference the first ten columns of a matrix A using
A[,1:10].
```{r}
pairs(college[,1:10])

```

iii. Use the plot() function to produce side-by-side boxplots of
Outstate versus Private.
```{r}
plot(College$Private,college$Outstate,xlab = "Private University", ylab = "Tuition in $",col = c("red","green"))
```

iv. Create a new qualitative variable, called Elite, by binning
the Top10perc variable. We are going to divide universities
into two groups based on whether or not the proportion
of students coming from the top 10 % of their high school
classes exceeds 50 %.
```{r}
Elite <- rep("No", nrow(college))
Elite[college$Top10perc > 50] <- "Yes"
Elite <- as.factor(Elite)
college <- data.frame(college, Elite)
```
Use the summary() function to see how many elite universities there are. 
```{r}
summary(college$Elite)
```

Now use the plot() function to produce side-by-side boxplots of Outstate versus Elite.
```{r}
plot(college$Elite, college$Outstate, 
     xlab = "Elite University", ylab = "Tuition in $", col=c("Blue","Red"))
```

v. Use the hist() function to produce some histograms with
differing numbers of bins for a few of the quantitative variables. You may find the command par(mfrow=c(2,2)) useful:it will divide the print window into four regions so that four
plots can be made simultaneously. Modifying the arguments
to this function will divide the screen in other ways.
```{r}
par(mfrow=c(2,2))
hist(college$Accept, xlab = "Applications Accepted", main = "")
hist(college$perc.alumni, col=2, xlab = "% of alumni who donate", main = "")
hist(college$S.F.Ratio, col=3, breaks=10, xlab = "Student/faculty ratio", main = "")
hist(college$Expend, breaks=100, col=7,xlab = "Instructional expenditure per student", main = "")
```

vi. Continue exploring the data, and provide a brief summary
of what you discover.
```{r}
# what is the university with the most students in the top 10% of class
row.names(college)[which.max(college$Top10perc)]  
#Acceptance Rate
acceptance_rate <- college$Accept / college$Apps

# what university has the Highest acceptance rate
row.names(college)[which.max(acceptance_rate)]  
```



10. This exercise involves the Boston housing data set.
(a) To begin, load in the Boston data set. The Boston data set is
part of the MASS library in R.
```{r}
library(MASS)
?Boston
attach(Boston)
```

Now the data set is contained in the object Boston.
How many rows are in this data set? How many columns?
```{r}
dim(Boston)
```

What do the rows and columns represent?
```{r}
#Each row represent the set of predictor obeservations for a given Neighborhood in Boston. Each column represent each predictor variable for which an observation was made in 506 neighborhoods of Boston.
```

(b) Make some pairwise scatterplots of the predictors (columns) in
this data set. Describe your findings.
```{r}
pairs(Boston)
```

(c) Are any of the predictors associated with per capita crime rate?
If so, explain the relationship.
```{r}
plot(Boston$crim ~ Boston$age,
     log = 'xy',
     col = 'steelblue')
#age: As the proportion of owner-occupied units built prior to 1940 increases, the Per Capita Crime Rate increases.
```


```{r}
plot(Boston$crim ~ Boston$dis,
     log = 'xy',
     col = 'green')
#dis: As the weighted mean of distances to five Boston employment centres increases, the Per Capita Crime Rate decreases.
```


```{r}
plot(Boston$crim ~ Boston$lstat,
     log = 'xy',
     col = 'red')

#lstat: As the lower status of the population (percent) increases, the Per Capita Crime Rate increases.
```

(d) Do any of the suburbs of Boston appear to have particularly
high crime rates? Tax rates? Pupil-teacher ratios? Comment on
the range of each predictor.
```{r}
hist(Boston$crim, breaks=25, col = "steelblue", main = "Histogram of Per Capita Crime Rate")
#There are very few Boston suburbs with high crime rates.
```

```{r}
hist(Boston$tax, breaks=25)
# there is a large divide between suburbs with low tax rates and a peak at 660-680
```


```{r}
hist(Boston$ptratio, breaks=25)
```

(e) How many of the suburbs in this data set bound the Charles
river?
```{r}
sum(chas == 1)
```
(f) What is the median pupil-teacher ratio among the towns in this
data set?
```{r}
summary(ptratio)
```

(g) Which suburb of Boston has lowest median value of owneroccupied homes? What are the values of the other predictorsfor that suburb, and how do those values compare to the overall
ranges for those predictors? Comment on your findings.
```{r}
t(subset(Boston, medv == min(medv)))

summary(Boston)

#Based on the list above, suburb 399 can be classified as one of the least desirable places to live in Boston.
```

(h) In this data set, how many of the suburbs average more than
seven rooms per dwelling? More than eight rooms per dwelling?
Comment on the suburbs that average more than eight rooms
per dwelling.
```{r}
sum(rm > 7)
```


```{r}
sum(rm > 8)
```


```{r}
dwelling_selection = subset(Boston, rm > 8)
summary(dwelling_selection)

```

